\section{Menus}
\subsection{File menu}

\begin{itemize}
\item \textbf{Open:} Loads a file and initiates a new \espina{} session.
\item \textbf{Add:} Loads and adds a file to the current session.
\item \textbf{Save:} Saves current session data to a SEG file.
\end{itemize}

\subsection{Analysis menu}

\begin{itemize}
\item \textbf{Segmentation information:} Toggles visibility of the ``Segmentation Information'' widget.
\end{itemize}

\subsection{Edit menu}

\begin{itemize}
\item \textbf{Undo:} Undo the last action.
\item \textbf{Redo:} Redo the last action removed by the undo function.
\end{itemize}

\subsection{View menu}

\begin{itemize}
\item \textbf{Panels:} Toggles the visibility of the following widgets:
	\begin{itemize}
	\item \textbf{Channel Explorer}
	\item \textbf{Filter Explorer}
	\item \textbf{Segmentation Explorer}
	\item \textbf{Taxonomy Explorer}
	\end{itemize}
\item \textbf{Color by:} Colorizes segmentations using one of the following criteria:
	\begin{itemize}
	\item \textbf{Taxonomy}
	\item \textbf{User}
	\item \textbf{Segmentation Id}
	\end{itemize}
\item \textbf{Views:} Toggles the visibility of the following planar view widgets:
	\begin{itemize}
	\item \textbf{XY:} Axial view.
	\item \textbf{XZ:} Coronal view.
	\item \textbf{YZ:} Sagittal view.
	\end{itemize}
\item \textbf{Show ruler:} Toggles the visibility of the size ruler over the planar views. The size unit is nanometers.
\item \textbf{Show thumbnail:} Toggles the visibility of the zoom thumbnail over the planar views.
\item \textbf{Switch channel:} Switches active channel function between loaded channels.
\item \textbf{Fit to slices:} Toggles the use of slicing step. When active the slice movement step in the planar views is the defined value of the image (in nanometers).
When not active the planar view allows free movement up to one nanometer in resolution.
\end{itemize}

\subsection{Settings menu}

\begin{itemize}
\item \textbf{Configure \espina:} Shows \espina{} configuration dialog.
\item \textbf{About:} Shows \espina{} about dialog.
\end{itemize}

\begin{bclogo}[couleur = yellow!33, logo=\bcattention]
{Note} Plugins can add items to menus. Refer to the plugin documentation for information.
\end{bclogo}
